---
title: " RealEstate_Poc"
output: 
  flexdashboard::flex_dashboard:
     logo: homes5.png
    
---

```{r setup, include=FALSE}
library(ggplot2)
library(plotly)
library(plyr)
library(flexdashboard)
library(xlsx)
library(knitr)
library(d3heatmap)
library(highcharter)

```


---

Current Month {data-navmenu="House Prices_CurrentMonth"}
=====================================
row
-----------------------------------------------------------------------




### current month zhvi

```{r}
library(xlsx)
currmonth <- read.xlsx("currentmonthsummary.xlsx",sheetIndex = 1)
czhvi<-currmonth$Zhvi
valueBox(czhvi, 
         icon = "fa-trash",
         color = ifelse(czhvi > 10, "warning", "primary"))
```

row
-----------------------------------
### current month qurter growth

```{r}
qval<-currmonth$QoQ
qgrowth<-qval*100
qgrowth<-round(qgrowth,2)
gauge(qgrowth, min = 0, max = 50, gaugeSectors(
  success = c(41, 50), warning = c(21, 40), danger = c(0, 20)
))
```

row
-----------------------------------
### current year growth

```{r}
yval<-currmonth$YoY
ygrowth<-yval*100
ygrowth<-round(ygrowth,2)
gauge(ygrowth, min = 0, max = 50, gaugeSectors(
  success = c(41, 50), warning = c(21, 40), danger = c(0, 20)
))
```





<!-- row -->
<!-- ----------------------------------- -->
<!-- ### current month MOM -->

<!-- ```{r} -->
<!-- county<-read.xlsx("countysummary.xlsx",sheetIndex = 1) -->
<!--  counties<-county$RegionName -->
<!--  mom<-county$MoM -->
<!--  yoy<-county$YoY -->
<!-- allvalues1<-data.frame(counties,mom,yoy) -->
<!-- p <- ggplot(allvalues1, aes(x=counties, y=mom, group=yoy)) + -->
<!--     geom_line() + -->
<!--     geom_point() -->

<!-- p <- ggplotly(p) -->

<!-- ``` -->







Single Family {data-navmenu="House Price Time Series"}
===================================== 
Row {data-height=600}
--------------------------
### County wise home values for all yeasr






```{r}
countyallyears <- read.csv("Countywiseallyears.csv",row.names=1)

d3heatmap(countyallyears, scale = "column",width=2000)

```

Row {data-height=600}
--------------------------
### County wise home values for current year
```{r}
countycurryear <- read.csv("CountyCurrentyear.csv")
data(countycurryear)
hc <- highchart() %>% 
  hc_xAxis(categories = countycurryear$RegionName) %>% 
  hc_add_series(name = "Home_2016_1", data = countycurryear$home_2016.01) %>% 
  hc_add_series(name = "home_2016.02", data = countycurryear$home_2016.02) %>% 
   hc_add_series(name = "home_2016.03", data = countycurryear$home_2016.03) %>% 
   hc_add_series(name = "home_2016.04", data = countycurryear$home_2016.04) %>% 
   hc_add_series(name = "home_2016.05", data = countycurryear$home_2016.05) %>% 
   hc_add_series(name = "home_2016.06", data = countycurryear$home_2016.06) %>% 
   hc_add_series(name = "home_2016.07", data = countycurryear$home_2016.07) %>% 
   hc_add_series(name = "home_2016.08", data = countycurryear$home_2016.08) %>% 
   hc_add_series(name = "home_2016.09", data = countycurryear$home_2016.09) %>% 
   hc_add_series(name = "home_2016.10", data = countycurryear$home_2016.10) %>% 
   hc_add_series(name = "home_2016.11", data = countycurryear$home_2016.11) %>% 
   hc_add_series(name = "home_2016.12", data = countycurryear$home_2016.12)
  hc

```



<!-- Row {data-height=600} -->
<!-- -------------------------- -->
<!-- ### County wise home values for current year -->
<!-- ```{r} -->
<!-- countycurryear <- read.csv("Countywiseallyears.csv") -->
<!-- data(countycurryear) -->

<!-- hc <- highchart() %>%  -->
<!--   hc_xAxis(categories = citytemp$month) %>%  -->
<!--   hc_add_series(name = "Tokyo", data = citytemp$tokyo) %>%  -->
<!--   hc_add_series(name = "London", data = citytemp$london) %>%  -->
<!--   hc_add_series(name = "Other city", -->
<!--                 data = (citytemp$tokyo + citytemp$london)/2) -->

<!-- ``` -->

Condo/Co {data-navmenu="House Price Time Series"}
=====================================  

1_BH's {data-navmenu="House Price Time Series"}
===================================== 

2_BH's {data-navmenu="House Price Time Series"}
=====================================

<!-- 3_BH's {data-navmenu="House Price Time Series"} -->
<!-- =====================================   -->

<!-- 4_BH's {data-navmenu="House Price Time Series"} -->
<!-- =====================================   -->

<!-- 5 or more BH's {data-navmenu="House Price Time Series"} -->
<!-- =====================================  -->

<!-- Median value per Sft {data-navmenu="House Price Time Series"} -->
<!-- =====================================   -->




Single Family {data-navmenu="Rental Price Time Series"}
=====================================


Condo/Co  {data-navmenu="Rental Price Time Series"}
=====================================

1_BH's {data-navmenu="Rental Price Time Series"}
=====================================

2_BH's {data-navmenu="Rental Price Time Series"}
=====================================
<!-- 3_BH's {data-navmenu="Rental Price Time Series"} -->
<!-- ===================================== -->

<!-- 4_BH's {data-navmenu="Rental Price Time Series"} -->
<!-- ===================================== -->

<!-- 5 or more BH's {data-navmenu="Rental Price Time Series"} -->
<!-- ===================================== -->

<!-- Median value per Sft {data-navmenu="Rental Price Time Series"} -->
<!-- ===================================== -->






page-1 {data-navmenu="Forecasting"}
=====================================






<!-- # Sidebar1 {.sidebar} -->
<!-- ================================================= -->


<!-- This dashboard covers several topics: -->

<!-- * House Prices_CurrentMonth -->
<!-- * House Price Time Series -->
<!-- * Rental Price Time Series -->