---
title: " Real Estate"
output: 
  flexdashboard::flex_dashboard:

   orientation: rows
   
   
---



<style type="text/css">


.chart-title {  /* chart_title  */
   font-size: 20px;
   display:        inline;
   font-family: Verdana;
  font-style: bold;
 
   }
  
 .nav-tabs-custom > .nav-tabs > li > a {
  border-top-color: white;
  border-right-color: white;
  border-left-color: blue;
   font-size: 20px;
    font-family: Verdana;
    font-style: bold;
  
 }
 .pager li > a,
.pager li > span {
  display: inline-block;
  padding: 5px 14px;
  background-color: #ffffff;
  border: 1px solid #dddddd;
  border-radius: 0;
  order-top-color: white;
  border-right-color: white;
  border-left-color: blue;
}
.pagination {
  display: inline-block;
  padding-left: 0;
  margin: 21px 0;
  border-radius: 10;
}
 
</style>



```{r}

library(flexdashboard)
library(knitr)
library(viridisLite)
library(highcharter)
library(plotly)
library(plyr)
library(RMySQL)
library(DBI)
library(sqldf)
library(gsubfn)
library(proto)
library(rsconnect)
library(stringr)
```

---

CurrentMonth House Prices
=====================================
row 1
-----------------------------------------------------------------------

### Home Value
```{r}

  db <- dbConnect(SQLite(), dbname='Test1.sqlite')
hCurMonth<-dbReadTable(db, 'current-month-summary')

hCurMonVal<-hCurMonth$Zhvi
valueBox(hCurMonVal,
         icon = "fa fa-dollar",
         color = ifelse(hCurMonVal > 10, "warning", "primary"))
```

### Current Month Growth
```{r}
library(flexdashboard)
hCurMonGro<-hCurMonth$MoM
hCurMonGro<-round((hCurMonGro*100),2)
gauge(hCurMonGro, min = 0, max = 4, symbol = "%",
      gaugeSectors(success = c(2, 4), warning = c(1, 2), danger = c(0, 1)
))
```

### Current Quarter Growth
```{r}

hQuGro<-hCurMonth$QoQ
hQuGro<-round(hQuGro*100,2)
gauge(hQuGro, min = 0, max = 7, symbol = "%",
      gaugeSectors(success = c(4, 5), warning = c(2, 3), danger = c(1, 2)))
```

### Current Year Growth
```{r}

hYeVal<-hCurMonth$YoY
hYeGrowth<-round(hYeVal*100,2)
gauge(hYeGrowth, min = 0, max = 10, symbol = "%",
      gaugeSectors(success = c(6, 10), warning = c(3, 5), danger = c(0, 2)))

```

### Peak Home Value
```{r}

hCurPekVal<-hCurMonth$PeakZHVI
valueBox(hCurPekVal,
         icon = "fa fa-long-arrow-up",
         color = ifelse(hCurMonVal > 10, "warning", "primary"))

```

ROW
--------------------------

### Top Metro
```{r}

#hCurrMonMet<-read.csv("metroCurrMon.csv")
hCurrMonMet<-dbReadTable(db, 'metro_current_month')
hTopMetro<-hCurrMonMet$RegionName[1]
hTopMetVal<-hCurrMonMet$Zhvi[1]/1000
valueBox(hTopMetro,icon = "fa fa-hand-o-left",paste0("Top Metro:$  ",hTopMetVal, "K"),color = "danger")
```

###Top County
```{r}

#hCurMonCou<-read.csv("countycurmnth.csv")
hCurMonCou<-dbReadTable(db,'county-current-month')
hCurMonCouTop<-max(hCurMonCou$Zhvi)
# hCurMonCou$Zhvi<-sort(hCurMonCou$Zhvi)
hCurMonCouTop<-hCurMonCouTop/1000
hTopCounty<-hCurMonCou$RegionName[1]
valueBox(hTopCounty,icon = "fa-pencil", paste0("Top County:$  ",hCurMonCouTop,"K"),color="green")

```

###Top City
```{r}

#hCurMonCity<-read.csv("citycurmnth.csv")
hCurMonCity<-dbReadTable(db,'city-current-month')
hTopCityValue<-max(hCurMonCity$Zhvi)
# hCurMonCity$Zhvi<-sort(CityCM$Zhvi)
hCurMonCityVal<-hTopCityValue/1000
hCurMonTopCity<-hCurMonCity$RegionName[1]
valueBox(hCurMonTopCity,icon = "fa fa-hand-o-left", paste0("Top City:$   ",hTopCityValue,"K"),color="blue"
         )
```

row 
----------
###  Counties Home Values
```{r}
library(highcharter)
#hCurMonCounty <- read.csv("county_cuurentmnth_HVandPHV.csv")
#data(countycurrmnth)
hCurMonCounty<-dbReadTable(db,'county_currentmnth_HVandPHV')
hc <- highchart() %>% 
   hc_yAxis(
    title = list(text = "Home Values")
    
  ) %>% 
  
  hc_xAxis(categories = hCurMonCounty$RegionName,
           title = list(text = "Region Names")) %>% 
    hc_add_series(name = "Home_Value", data = hCurMonCounty$Zhvi) %>% 
   hc_add_series(name = "Peak_Home_Value", data = hCurMonCounty$PeakZHVI)
  hc
```


### Metros Home Values
```{r}
library(highcharter)
hCurrMonMetro<-dbReadTable(db,'metro-single1')


hc <- highchart() %>% 
  hc_chart(type = "column") %>%
   hc_yAxis(
    title = list(text = "Home Values")
    
  ) %>% 
  
  hc_xAxis(categories = hCurrMonMetro$RegionName,
           title = list(text = "Region Names")) %>% 
    hc_add_series(name = "Home_Value", data = hCurrMonMetro$AHV_2017) 
  
  hc
```


CurrentMonth Rental Prices
=====================================
ROW
---------------------------------------
###  Rental Value
```{r}

rCurMonth<-dbReadTable(db,'current-month-state-zri')
rCurMonVal<-rCurMonth$Zri
valueBox(rCurMonVal,icon = "fa-dollar", color = ifelse(rCurMonVal > 10, "warning", "primary"))
```

### Current Month Rental Growth
```{r}
rCurMonGro<-rCurMonth$MoM
rCurMonGro<-round((rCurMonGro*100),2)
gauge(rCurMonGro, min = 0, max = 4, symbol = "%",
      gaugeSectors(success = c(2, 4), warning = c(1, 2), danger = c(0, 1)
))
```

### Current Qurter Rental Growth
```{r}
rCurMonQuVal<-rCurMonth$QoQ
rCurMonQuVal<-round(rCurMonQuVal*100,2)
gauge(rCurMonQuVal, min = 0, max = 5, symbol = "%",
      gaugeSectors(success = c(3, 5), warning = c(1, 3), danger = c(0, 1)))
```

### Current Year Rental Growth
```{r}
rcurMonYeVal<-rCurMonth$YoY
rcurMonYeVal<-round(rcurMonYeVal*100,2)

gauge(rcurMonYeVal, min = 0, max = 10, symbol = "%",
      gaugeSectors(success = c(6, 10), warning = c(3, 5), danger = c(0, 2)))
```

ROW
--------------------------

### Top Metro
```{r}
#rCurMonMetro<-read.csv("metrocurr_zri.csv")
rCurMonMetro<-dbReadTable(db,'metro_current-zri')
rCurMonTopMetro<-rCurMonMetro$RegionName[1]
rCurMonTopMetVal<-rCurMonMetro$Zri[1]
valueBox(rCurMonTopMetro,icon = "fa fa-hand-o-left",paste0("Top Metro:$   ",rCurMonTopMetVal),color = "purple")

```

###Top County
```{r}
#rCurMonCounty<-read.csv("county_rental_zri.csv")
rCurMonCounty<-dbReadTable(db,'county-rental-zri')
rCurMonTopCouVal<-rCurMonCounty$Zri[1]
rCurMonTopCounty<-rCurMonCounty$RegionName[1]
valueBox(rCurMonTopCounty,icon = "fa-pencil", paste0("Top County:$   ",rCurMonTopCouVal),color="green")
```

###Top City
```{r}
#rCurMonCity<-read.csv("Citywise_rental_Zri.csv")
rCurMonCity<-dbReadTable(db, 'city_wise_rental-Zri')
rCurMonTopCityVal<-rCurMonCity$Zri[1]
rCurMonTopCity<-rCurMonCity$RegionName[1]
valueBox(rCurMonTopCity,icon = "fa fa-hand-o-left", paste0("Top City:$   ",rCurMonTopCityVal),color="blue")
```

Row 
-------------------------------------
### Cities Rental Values
```{r}
#rCurMonCitySF<-read.csv("cityrentalSFR.csv")
rCurMonCitySF<-dbReadTable(db,'city-rental-SFR')

highchart() %>%
 hc_chart(type = "area") %>%
  
  hc_xAxis(categories=rCurMonCitySF$RegionName,title = list(text = "Region Names")) %>%
   hc_yAxis(
    title = list(text = "Rental Values")
    
  ) %>% 
 hc_add_theme(hc_theme_sandsignika())%>%
  hc_add_series(name = "2012", data =rCurMonCitySF$Avg2012) %>%
 
  hc_add_series(name = "2013", data = rCurMonCitySF$Avg2013) %>%
  hc_add_series(name = "2014",data = rCurMonCitySF$Avg2014) %>%
  hc_add_series(name = "2015",data = rCurMonCitySF$Avg2015) %>%
  hc_add_series(name = "2016",data = rCurMonCitySF$Avg2016)
```

### Metros Rental Values
```{r}

rCurMonMet<-dbReadTable(db,'metro_current-zri')

 highchart() %>%
 hc_chart(type = "area") %>%
  
  hc_xAxis(categories=rCurMonMet$RegionName,title = list(text = "Region Names")) %>%
   hc_yAxis(
    title = list(text = "Rental Values")
    
  ) %>% 
 hc_add_theme(hc_theme_sandsignika())%>%
  hc_add_series(name = "Rental Values", data =rCurMonMet$Zri)
 


```


Single Family Residences {data-navmenu="House Prices"}
===================================== 
row
--------------------------
### Current Year Top County in Growth
```{r}
CCM<-dbReadTable(db,'county-current-month')
topyoy<-round(max(CCM$YoY)*100,2)
gauge(topyoy, min = 0, max = 50, symbol="%",label = paste0("Siskiyou "),
      gaugeSectors(success = c(30, 50), warning = c(20, 30), danger = c(0, 20)
))
```

### Current Quarter Top County in Growth
```{r}
topqoq<-round(max(CCM$QoQ)*100,2)
gauge(topqoq, min = 0, max = 10, symbol="%",label = paste("TopQGrowth:Marin"),gaugeSectors(
  success = c(6, 10), warning = c(3, 6), danger = c(0, 3)
))
```

### Current Month Top County in Growth
```{r}
topmom<-round(max(CCM$MoM)*100,2)
gauge(topmom, min = 0, max = 5, symbol="%",label = paste("TopGrowth:Mariposa"),gaugeSectors(
  success = c(4, 5), warning = c(2, 4), danger = c(0, 2)
))
```


Row {.tabset .tabset-fade}
-------------------------------------
###  Cities Home Values 

```{r}

#book<-read.csv("citywise_HV_allyears_single.csv")
book<-dbReadTable(db,'City-wise-HV-allyears-single')

hc <- highchart() %>% 
  hc_xAxis(categories =book$RegionName,
 title = list(text = "Region Names"))%>% 
  hc_yAxis(
    title = list(text = "Home Values")
    
  ) %>% 
  hc_subtitle(text = "Average Home Values") %>% 
  
   hc_add_series(name = "2012", data = book$AHV_2012) %>% 
   hc_add_series(name = "2013", data = book$AHV_2013) %>% 
   hc_add_series(name = "2014", data = book$AHV_2014) %>% 
   hc_add_series(name = "2015", data = book$AHV_2015) %>% 
   hc_add_series(name = "2016", data = book$AHV_2016)  
   
   hc
```

### Average Home Values for Counties

```{r}
#countyallyearsheat <- read.csv("Countywiseallyearsheat.csv",row.names=1)
countyallyearsheat<-dbReadTable(db,'county_wise-allyear-sheat')

m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)
y <- list(
  title = "Home  Values"
 
)
x <- list(
  title = "Region Names"
 
)
RegionNames<-as.list(countyallyearsheat$RegionName)
y2012<-as.list(countyallyearsheat$y2012)
y2013<-as.list(countyallyearsheat$y2013)
y2014<-as.list(countyallyearsheat$y2014)
y2015<-as.list(countyallyearsheat$y2015)
y2016<-as.list(countyallyearsheat$y2016)
plot_ly(countyallyearsheat
        , x = ~RegionNames) %>%
   add_paths(y=~y2012, name = "2012", visible = T) %>%
  add_paths(y=~y2013, name = "2013") %>%
  add_paths(y=~y2014, name = "2014", visible = T) %>%
  add_paths(y=~y2015, name = "2015", visible = T) %>%
     add_paths(y=~y2016, name = "2016", visible = T) %>%
  layout(autosize = F, width = "1000px", height = "1000px", margin = m,x_axis=x,yaxis=y,title="Average Home Values")


```


1 BH's {data-navmenu="House Prices"}
===================================== 

ROW {.tabset .tabset-fade}
---------------------------

###   Counties Home Values 
```{r}
#county_1BH<-read.csv("countywise_1BH.csv")
county_1BH<-dbReadTable(db,'county_wise_1BH')

highchart() %>%
 hc_chart(type="column") %>%
  
  hc_xAxis(categories=county_1BH$RegionName,
            title = list(text = "Region Names")) %>%
   hc_yAxis(
    title = list(text = "Home Values")
    
  ) %>%
  hc_subtitle(text = "Average Home Values") %>% 
hc_add_series(name = "2012", data =county_1BH$Avr_coHV_2012,type = "column",color="red") %>%
  hc_add_series(name = "2013", data = county_1BH$Avg_coHV_2013,type = "column",color="blue") %>%
  hc_add_series(name = "2014",data = county_1BH$Avg_coHV_2014,type = "column",color="yellow") %>%
  hc_add_series(name = "2015",data = county_1BH$Avg_coHV_2015,type = "column",color="navy") %>%
  hc_add_series(name = "2016",data = county_1BH$Avg_coHV_2016,type = "column",color="green")

```

### Growth of Counties
```{r}
library(highcharter)
# MA1BH<-read.csv("metrowise1BH.csv")
MA1BH<-dbReadTable(db,'metro-wise-1Bh')

hc<-highchart() %>%
 hc_chart(type="column") %>%
 hc_xAxis(categories=MA1BH$RegionName.,
           title = list(text = "Region Names")) %>%
         
   hc_yAxis(
    title = list(text = "Home Values")
    
  ) %>% 
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_subtitle(text = " Growth Values ") %>% 
  hc_add_series(name = "2012", data =MA1BH$PerGrowth_2013,type = "line",color="red") %>%
  hc_add_series(name = "2014",data = MA1BH$PerGrowth_2014,type = "line",color="yellow") %>%
  hc_add_series(name = "2015",data = MA1BH$PerGrowth_2015,type = "line",color="navy") %>%
  hc_add_series(name = "2016",data = MA1BH$PerGrowth_2016,type = "line",color="green")
hc

```


ROW {.tabset .tabset-fade}
---------------------------
###  Cities Home Values
```{r}
#citywise1BH<-read.csv("citywise1BH.csv")
citywise1BH<-dbReadTable(db,'city-wise-1BH')



hc <- highchart() %>% 
  hc_yAxis(
    title = list(text = "Home Values")
    
  ) %>% 
  hc_xAxis(categories = citywise1BH$RegionName,
           title = list(text = "Region Names")) %>% 
  hc_add_series(name = "2012", data = citywise1BH$Avg_ciHV_2012,color="purple") %>% 
  hc_subtitle(text = "Average Home Values") %>% 
  hc_add_series(name = "2013", data = citywise1BH$Avg_ciHV_2013,color="green") %>% 
   hc_add_series(name = "2014", data = citywise1BH$Avg_ciHV_2014,color="yellow") %>% 
   hc_add_series(name = "2015", data = citywise1BH$Avg_ciHV_2015,color="blue") %>% 
   hc_add_series(name = "2016", data = citywise1BH$Avg_ciHV_2016,color="olive") 
  # hc_chart(type = "column",
  #          options3d = list(enabled = TRUE, beta = 15, alpha = 15))

  

hc
```


2 BH's {data-navmenu="House Prices"}
=====================================
Row {.tabset .tabset-fade}
-------------------------------------
###  Counties Home Values 
```{r}

#county_2bh<-read.csv("countywise2BH.csv")
county_2bh<-dbReadTable(db,'county-wise-2BH')

highchart() %>%
 hc_chart(type="column") %>%
  hc_chart(type = "column",
           options3d = list(enabled = TRUE, beta = 5, alpha = 5)) %>%

  hc_xAxis(categories=county_2bh$RegionName,
            title = list(text = "Region Names")) %>%
   hc_yAxis(
    title = list(text = "Home Values")
    
  ) %>% 
hc_add_series(name = "2012", data =county_2bh$HV2012,type = "column",color="red") %>%
  hc_add_theme(hc_theme_538()) %>%
  hc_subtitle(text = "Average Home Values") %>% 
  hc_add_series(name = "2013", data = county_2bh$HV2013,type = "column",color="blue") %>%
  hc_add_series(name = "2014",data = county_2bh$HV2014,type = "column",color="yellow") %>%
  hc_add_series(name = "2015",data = county_2bh$HV2015,type = "column",color="navy") %>%
  hc_add_series(name = "2016",data = county_2bh$HV2016,type = "column",color="green")


```


column {.tabset .tabset-fade}
------------------------------

###  Counties Growth values
```{r}
#county_2bh<-read.csv("countywise2BH.csv")
county_2bh<-dbReadTable(db,'county-wise-2BH')
hc <- highchart() %>% 
  hc_xAxis(categories = county_2bh$RegionName,title = list(text = "Region Names")) %>%
  hc_yAxis(
    title = list(text = "Home Values")
    
  ) %>% 
hc_subtitle(text = "Average Growth Values") %>% 
  hc_add_series(name = "2013", data = county_2bh$PctGrowth_2013) %>% 
  hc_add_series(name = "2014", data = county_2bh$PctGrowth_2014) %>% 
  hc_add_series(name = "2015", data = county_2bh$PctGrowth_2015) %>% 
  hc_add_series(name = "2016", data = county_2bh$PctGrowth_2016)
hc

```

### Metros Homes Values 
```{r}

df<-dbReadTable(db,'city-wise-2BH')
highchart() %>%
  hc_chart(type = "bubble") %>%
  hc_xAxis(categories=df$RegionName,title = list(text = "Region Names")) %>%
  hc_yAxis(
    title = list(text = "Home Values")
    
  ) %>% 
  hc_subtitle(text = "Average Home Values") %>% 
  hc_add_series(name = "2012", data =df$Avg_city_2BH_2012) %>%
  hc_add_series(name = "2013", data = df$Avg_city_2bh_2013) %>%
  hc_add_series(name = "2014",data = df$Avg_city_2014) %>%
  hc_add_series(name = "2015",data = df$Avg_city_2015) %>%
  hc_add_series(name = "2016",data = df$Avg_city_2016)
```




Single Family {data-navmenu="Rental Prices"}
===================================== 
ROW 
------------------------------
###  Metros Rental Values 

```{r}

 ren_Met_Sfr<-dbReadTable(db,'Metro-Rental-SFR')

highchart() %>%
  hc_chart(type = "bubble") %>%
  hc_yAxis(
    title = list(text = "Rental Values")
    
  ) %>% 
  hc_xAxis(categories=ren_Met_Sfr$RegionName,title = list(text = "Region Names")) %>%
  hc_subtitle(text = "Average Rental Values") %>% 
  hc_add_series(name = "2012", data =ren_Met_Sfr$Avg_Met_SFR_2012) %>%
  hc_add_series(name = "2013", data = ren_Met_Sfr$Avg_Met_SFR_2013) %>%
  hc_add_series(name = "2014",data = ren_Met_Sfr$Avg_Met_SFR_2014) %>%
  hc_add_series(name = "2015",data = ren_Met_Sfr$Avg_Met_SFR_2015) %>%
  hc_add_series(name = "2016",data = ren_Met_Sfr$Avg_Met_SFR_2016)
```



### Counties Rental Values 
```{r}

CRSFR<-dbReadTable(db, 'county_ZRISFR')

plot_ly(CRSFR, labels = CRSFR$RegionName, values = CRSFR$Avg2016, type = "pie",name = "Avg2012", showlegend = T) %>%
  layout(title = "Rental Values For Single Home Residency(2016)",xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

1 BH's {data-navmenu="Rental Prices"}
=====================================
Row {.tabset .tabset-fade}
-------------------------------------

### Counties Rental Growth 
```{r}
#county<-read.csv("rental_coun_1bh.csv")
county<-dbReadTable(db,'rental-county-1BH')
region<-as.list(county$RegionName)
Growth_2012<-as.list(county$per_12)
Growth_2013<-as.list(county$per_13)
Growth_2014<-as.list(county$per_14)
Growth_2015<-as.list(county$per_15)
Growth_2016<-as.list(county$per_16)
hc<-highchart() %>%
 hc_chart(type="column") %>%
  hc_xAxis(categories =county$RegionName,title = list(text = "Region Names")) %>%
  hc_yAxis(
    title = list(text = "Rental Values")
    
  ) %>% 
  hc_subtitle(text = "Average Growth Values") %>% 

  hc_add_theme(hc_theme_darkunica())%>%
  hc_add_series(name = "2012", data = county$per_12) %>% 
  hc_add_series(name = "2013", data = county$per_13) %>% 
   hc_add_series(name = "2014", data = county$per_14) %>% 
   hc_add_series(name = "2015", data = county$per_15) %>% 
   hc_add_series(name = "2016", data = county$per_16) 
hc
```


###  Cities Rental Values
```{r }

rental_1BH<-dbReadTable(db, 'rental-1BH')
Rental_Values<-rental_1BH$RV_2012
m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)
y <- list(
  title = "Rental Values"
 
)
x <- list(
  title = "Region Names"
 
)
plot_ly(rental_1BH, x = ~RegionName, y = ~Rental_Values) %>%
  add_bars(x = ~RegionName,                                        
            y = ~Rental_Values,
            name="2012",
            mode = 'bars',
           
            line = list(                                      
              color = "green"                             
                                            
            )
  ) %>%
  
  add_bars(x = ~RegionName,                                         
            y = ~RV_2013,
            name="2013",
            mode = 'bars',
           
            line = list(                                      
              color = "green"                          
                                              
            )
  ) %>%
  add_bars(x = ~RegionName,                                        
            y = ~RV_2014,
            name="2014",
            mode = 'bars',
           
            line = list(                                       
              color = "yellow"                               
                                            
            )
  ) %>%
  add_bars(x = ~RegionName,                                        
            y = ~RV_2015,
            name="2015",
            mode = 'bars',
           
            line = list(                                       
              color = "red"                           
                                             
            )
  ) %>%
  add_bars(x = ~RegionName,                                         
            y = ~RV_2016,
            name="2016",
            mode = 'bars',
           
            line = list(                           
              color = "black"                             
                                           
            )
  ) %>%
  layout(autosize = F, width = "400px", height = "200px", margin = m,x_axis=x,yaxis=y,title="Average Rental Values")

```



Row {.tabset .tabset-fade}
-------------------------------------
### Counties Rental Values 
```{r}

 db <- dbConnect(SQLite(), dbname='Test1.sqlite')
Rentalcounty1BH<-dbReadTable(db,'Rental')


region<-Rentalcounty1BH$RegionName
Ren1BH16<-Rentalcounty1BH$Rental_16
p<-plot_ly(Rentalcounty1BH,labels = ~region, values = ~Ren1BH16) %>%
  add_pie(hole = 0.6) %>%
  layout( showlegend = T,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
p
```

Top5 Rental and Home Values
=====================================
row {.tabset .tabset-fade}
----------------
### Top and Least 5 Metros Home Values
```{r}
MTLHV<-dbReadTable(db,'metro-top-low-homevalues')
MTHV<-data.frame(MTLHV[c(1:5),c(1,4,12)])
colnames(MTHV)<-c("RegionName","Zhvi","PeakZHVI")
MLHV<-data.frame(MTLHV[c(6:10),c(1,4,12)])
colnames(MLHV)<-c("RegionName","Zhvi","PeakZHVI")
p <- plot_ly() %>%
  add_pie(data = MTHV, labels = MTHV$RegionName, values = MTHV$Zhvi,hole = 0.6,
          name = "Top5Metros", domain = list(x = c(0, 0.4), y = c(0.4, 1))) %>%
  add_pie(data =MLHV , labels = MLHV$RegionName, values = MLHV$Zhvi,
          name = "Least5Metros", domain = list(x = c(0.6, 1), y = c(0.4, 1))) %>%

  layout(title = "Top and Least Metros", showlegend = T,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
p

```


###  Top and Least Metros Rental Values 
```{r}
top5metrorental<- dbReadTable(db,'rental-metro-top')

least5metrorental<- dbReadTable(db,'rental-metro-least')


p <- plot_ly() %>%
  add_pie(data = top5metrorental, labels = top5metrorental$RegionName, values = top5metrorental$Zri,hole = 0.6,
          name = "Top5Metros", domain = list(x = c(0, 0.4), y = c(0.4, 1))) %>%
  add_pie(data =least5metrorental , labels = least5metrorental$RegionName, values = least5metrorental$Zri,
          name = "Least5Metros", domain = list(x = c(0.6, 1), y = c(0.4, 1))) %>%
  
  layout(title = "Top and Least Metros", showlegend = T,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
p
```

Metro {data-navmenu="Forecasting"}
===================================== 
ROW 
----------
### Home Values Santa Cruz

```{r}

SantaCruz<-dbReadTable(db, 'SantaCruz') 

Cruz <- sample(1:nrow(SantaCruz),size = 0.8*nrow(SantaCruz)) 

trainCruz <- SantaCruz[Cruz,] 


testCruz <- SantaCruz [-Cruz,]


metroCruz<-lm(SantaCruz~Year+Months,trainCruz)

metroCruztestdata<-predict(metroCruz,testCruz)

metroSantaCruz <- predict(metroCruz)

newdata2<-data.frame(Year=c(2017),Months=c(1,2,3,4,5,6,7,8,9,10,11,12))

SantaCruzPredictedValues <- predict(metroCruz,newdata2)

predictedCruz<-dbReadTable(db, 'SantaCruz-Predicted-Values') 
pc<-dbReadTable(db,'SantaCruz-Predicted-Values')
month <- c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul',
               'Aug', 'Sep', 'Oct', 'Nov', 'Dec')
 
  pc<-cbind(pc,month) 
  

  pc$month <- factor(pc$month, levels = pc[["month"]])
#colnames(pc)<-c("Month","HomeValues","month")
 p <- plot_ly(pc, x = ~month, y = ~pc$HomeValues, name = ' HomeValues', type = 'scatter', mode = 'lines',
         marker = list(color = 'rgb(153, 0, 102 )')  ) %>%

 layout(
                                    xaxis = list(title = "Months"),
                                   yaxis = list (title = "Home Values "),
                                   barmode = 'relative')
                          
p
    
   

```

<!-- ### Home Values San Francisco  -->
<!-- ```{r} -->

<!-- metro_sanfrans<-dbReadTable(db,'predict') -->
<!-- hc <- highchart() %>% -->

<!--   hc_yAxis( -->
<!--     title = list(text = "Home Values") -->

<!--   ) %>%  -->


<!--    hc_add_series(name = "Home Values", data =metro_sanfrans$HomeValue) -->
<!--   hc -->


<!-- ``` -->


### Home Values Los Angeles
```{r}

metro_losangle<-dbReadTable(db, 'LosAngels-Predicted-Values') 

 month <- c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul',
               'Aug', 'Sep', 'Oct', 'Nov', 'Dec')
 
 
  metro_losangle<-cbind(metro_losangle,month)  

  metro_losangle$month <- factor(metro_losangle$month, levels = metro_losangle[["month"]])
  m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)
  y <- list(
  title = "Home Values"
 
)
x <- list(
  title = "Region Names"
 
)

 p <- plot_ly(metro_losangle, x = ~month, y = ~Home_Values,type="box",mode="markers", name = 'Home Values',color = "yellow") %>%
             

             layout(
                   xaxis = list(title = 'Months'),
                   yaxis = list(title = 'Home Values'),
                   linemode = 'relative',x_axis=x,yaxis=y)
    
              p
    
```

ROW 
---------
###  Home Values  Napa 
```{r}


napapredict<-dbReadTable(db,'Napa-predict')

p <- plot_ly() %>%
  add_pie(data = napapredict, labels = napapredict$Months, values = napapredict$HomeValues,hole = 0.6,
          name = "Napa Home Values", domain = list(x = c(0, 0.4), y = c(0.4, 1))) %>%
  layout( showlegend = T,
         xaxis = list(showgrid = TRUE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
p
```

###  Home Values San Jose
```{r}
sanjose<-dbReadTable(db, 'SanJose') 
sanjose1 <- sample(1:nrow(sanjose),size = 0.8*nrow(sanjose))

trainSJ <- sanjose[sanjose1,] 

testSJ <- sanjose[-sanjose1,]


sjlm<-lm(HomeValues~Year+Month,trainSJ)

testing<-predict(sjlm,testSJ)

sjpre<-predict(sjlm)

newdata<-data.frame(Year=c(2017),Month=c(1:12))

sjpre1<-predict(sjlm,newdata=newdata)
y <- list(
  title = "Home Values 2017"
 
)

predsjvalues<-dbReadTable(db,'SanJose-Predicted-Values')
sjpredvalues<-dbReadTable(db,'SanJose-Predicted-Values')
month <- c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul',
               'Aug', 'Sep', 'Oct', 'Nov', 'Dec')
 
  sjpredvalues<-cbind(sjpredvalues,month) 
  

  sjpredvalues$month <- factor(sjpredvalues$month, levels = sjpredvalues[["month"]])


plot_ly(sjpredvalues, x = ~sjpredvalues$month, y = ~sjpredvalues$HomeValues, color = ~sjpredvalues$month,
         text = ~paste("Month: ", sjpredvalues$month))%>%
   layout(
        
         yaxis = list(title ="Home Values"))

```





County {data-navmenu="Forecasting"}
===================================== 
row
-------------------
### Home Values Santa Clara
```{r}

santaclara<- dbReadTable(db,'SantaClaraData')

santaclarasample <- sample(1:nrow(santaclara),size = 0.8*nrow(santaclara))
trainSC <- santaclara[santaclarasample,] 
testSC <- santaclara[-santaclarasample,]
sclm<-lm(HomeValues~Year+Month,trainSC)
predictionsc<-predict(sclm,testSC)
scpre<-predict(sclm)

newdatasc<-data.frame(Year=c(2017),Month=c(1:12))
scpre1<-predict(sclm,newdata=newdatasc)
predscvalues<-dbReadTable(db,'SantaClara-Predicted-Values')

   scpredvalues<-dbReadTable(db,'SantaClara-Predicted-Values')

month <- c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul',
               'Aug', 'Sep', 'Oct', 'Nov', 'Dec')
 
scpredvalues<-cbind(scpredvalues,month) 
scpredvalues$month <- factor(scpredvalues$month, levels = scpredvalues[["month"]])
colnames(scpredvalues)<-c("x","HomeValues","month")
plot_ly(scpredvalues, x = ~scpredvalues$month, y = ~scpredvalues$HomeValues, 
        type = 'scatter', mode = 'lines',marker = list(color = ~scpredvalues$month)
        ,text = ~paste("Month: ", scpredvalues$month))%>%
        layout(
         xaxis = list(title ="Months"),
         yaxis = list(title ="Home Values"))
      
 
```


### Home Values Sanmateo
```{r}
sanmateo<-dbReadTable(db,'SanMateo-Data')
sanmateosample <- sample(1:nrow(sanmateo),size = 0.8*nrow(sanmateo)) 
trainsanmateo <- sanmateo[sanmateosample,] 
testsanmateo <- sanmateo [-sanmateosample,]
sanmateomodel<-lm(HomeValues~Year+Month,trainsanmateo)
sanmateopred<-predict(sanmateomodel,testsanmateo)
newdataSM<-data.frame(Year=c(2017),Month=c(1,2,3,4,5,6,7,8,9,10,11,12))
sanmateopredictedvalues <- predict(sanmateomodel,newdataSM)
sanmateopredictedvaluescsv<-dbReadTable(db,'SanMateo-predicted-values')
SMpredvalues<-dbReadTable(db,'SanMateo-predicted-values')
month <- c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul',
               'Aug', 'Sep', 'Oct', 'Nov', 'Dec')
 
 SMpredvalues<-cbind(SMpredvalues,month) 
SMpredvalues$month <- factor(SMpredvalues$month, levels = SMpredvalues[["month"]])
colnames(SMpredvalues)<-c("Month","HomeValues","month")
 p <- plot_ly(SMpredvalues, x = ~month, y = ~SMpredvalues$HomeValues, name = ' HomeValues', type ='scatter',
    mode="lines", marker = list(color = 'rgb( 147, 34, 141  )')  ) %>%
     layout(
           xaxis = list(title = "Months"),
          yaxis = list (title = "Home Values"),
          barmode = 'relative')

 p
    
``` 


row
----------

### Home Values Marin
```{r}
marin<-dbReadTable(db,'Marin-data')
 
marinsample <- sample(1:nrow(marin),size = 0.8*nrow(marin)) 
trainmarin <- marin[marinsample,] 

testmarin  <- marin [-marinsample,]
marinmodel<-lm(HomeValues~Year+Month,trainmarin)
marinpred<-predict(marinmodel,testmarin)

newdatamarin<-data.frame(Year=c(2017),Month=c(1,2,3,4,5,6,7,8,9,10,11,12))
marinpredictedvalues <- predict(marinmodel,newdatamarin)
marinpredictedvaluescsv<- dbReadTable(db,'Marin-predicted-values')
 marinpredvalues<-dbReadTable(db,'Marin-predicted-values')
 
month <- c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul',
               'Aug', 'Sep', 'Oct', 'Nov', 'Dec')
 
marinpredvalues<-cbind(marinpredvalues,month) 
marinpredvalues$month <- factor(marinpredvalues$month, levels = marinpredvalues[["month"]])
colnames(marinpredvalues)<-c("Month","HomeValues","month")
highchart() %>%
  hc_chart(type = "line") %>%
  hc_xAxis(categories=marinpredvalues$month) %>%
  hc_add_series(name = "Home Values", data =marinpredvalues$HomeValues,color = "#B71C1C") 

```


### Home Values Alabama


```{r}
alameda<-dbReadTable(db,'AlamedaData')
 alamedasample <- sample(1:nrow(alameda),size = 0.8*nrow(alameda)) 
trainalameda <- alameda[alamedasample,] 
testalameda  <- alameda [-alamedasample,]
alamedamodel<-lm(HomeValues~Year+Month,trainalameda)
alamedapred<-predict(alamedamodel,testalameda)

newdataalameda<-data.frame(Year=c(2017),Month=c(1,2,3,4,5,6,7,8,9,10,11,12))
alamedapredictedvalues <- predict(alamedamodel,newdataalameda)
alameda2017predvalues<- dbReadTable(db,'Alameda-Predicted-Values')
 
month <- c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul',
               'Aug', 'Sep', 'Oct', 'Nov', 'Dec')
 
alameda2017predvalues<-cbind(alameda2017predvalues,month) 
alameda2017predvalues$month <- factor(alameda2017predvalues$month, levels = alameda2017predvalues[["month"]])
colnames(alameda2017predvalues)<-c("x","HomeValues","month")

     highchart() %>% 
 
   
  hc_xAxis(categories = alameda2017predvalues$month) %>% 
  
  hc_add_series_labels_values(alameda2017predvalues$month, alameda2017predvalues$HomeValues, type = "column",
                              colorByPoint = TRUE, center = c('35%', '10%'),
                             size = 100, dataLabels = list(enabled = FALSE)) 
  
     
```


### Home Values San Francisco
```{r}
library(highcharter)
sanfrancisco<-dbReadTable(db,'SanFransiscoData')
sanfranciscosample <- sample(1:nrow(sanfrancisco),size = 0.8*nrow(sanfrancisco)) 
trainsanfrancisco <- sanfrancisco[sanfranciscosample,] 
testsanfrancisco  <- sanfrancisco [-sanfranciscosample,]
sanfranciscomodel<-lm(HomeValues~Year+Month,trainsanfrancisco)
sanfranciscopred<-predict(sanfranciscomodel,testsanfrancisco)

newdatasanfrancisco<-data.frame(Year=c(2017),Month=c(1,2,3,4,5,6,7,8,9,10,11,12))
sanfranciscopredictedvalues <- predict(sanfranciscomodel,newdatasanfrancisco)
sanfrancisco2017predvalues<- dbReadTable(db,'Sanfransisco-Predicted-Values')
 
month <- c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul',
               'Aug', 'Sep', 'Oct', 'Nov', 'Dec')
 
sanfrancisco2017predvalues<-cbind(sanfrancisco2017predvalues,month) 
sanfrancisco2017predvalues$month <- factor(sanfrancisco2017predvalues$month, levels = sanfrancisco2017predvalues[["month"]])
colnames(sanfrancisco2017predvalues)<-c("x","HomeValues","month")

highchart(width = 400, height = 400) %>% 
  
  
  hc_chart(type = "pie", options3d = list(enabled = TRUE, alpha = 70, beta = 0)) %>% 
  hc_plotOptions(pie = list(depth = 70)) %>% 
  hc_add_series_labels_values(sanfrancisco2017predvalues$month, sanfrancisco2017predvalues$HomeValues) %>% 
  hc_add_theme(hc_theme(
    chart = list(
      backgroundColor = NULL,
      divBackgroundImage = "https://media.giphy.com/media/Yy26NRbpB9lDi/giphy.gif"
    )
  ))
```